A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-17 paper.tex
Some corrections to 4d N=2 SUSY
Comment on 4d N=2

\part{A Catalogue of Twists}
\chris{We actually used this heading in our previous paper, so maybe a different name?}

@@

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
It will be enough for our purposes to describe only the action of a chiral supercharge.
\begin{prop} \label{4d_2_susy_action_prop}
After reduction to $\mr O(4)$, the 6d $\mc N=(1,0)$ interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_1^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
I^{(2)}_{\mr{matter}}(Q,Q) &= 0 %\frac 14 \dvol (Q_+,Q_+)(\psi_+,\psi_+)(w_+ \wedge w_+)
\end{align*}
if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
\end{prop}

@@

\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.}
\end{proof}

>>>>

\part{Classification of Twists}

@@

\vspace{-10pt}
\paragraph{Supersymmetry action:} 
It will be enough for our purposes to describe only the action of a chiral supercharge.
\begin{prop} \label{4d_2_susy_action_prop}
After reduction to $\mr O(4)$, the 6d $\mc N=(1,0)$ interaction terms $I^{(1)}$ and $I^{(2)}$ become
\begin{align*}
I^{(1)}_{\mr{gauge}}(Q) &= \int \dvol \bigg(-( (\Gamma(Q_+,\lambda_-)(w_+,u_-), A^*) + \langle Q_+,\lambda_+\rangle w_+ \wedge u_+, \phi_2^* ) + \\
&\qquad  + \frac 12 ((\rho(F_A)Q_+, \lambda_+^*)(u_+^*,  w_+) + (\rho(\d_A \phi_2(w_+ \wedge u_-^*))Q_+, \lambda_-^*) \bigg)\\
I^{(1)}_{\mr{matter}}(Q) &= \int \dvol (((Q_+,\psi_+), \phi^*)(v^*,w_+) + \frac 12 (\rho(\d_A \phi)Q_+, \psi_+^*)(v,w_+)) \\
I^{(2)}_{\mr{gauge}}(Q,Q) &= \int \dvol \big(\frac 14 (Q_+,Q_+)(\lambda_-,\lambda_-)(u_-,w_+)^2 - \frac 12  (Q_+, \lambda_-^*)^2(w_+ \wedge u_-^*)^2 - (Q_+,Q_+)\phi_1(w_+ \wedge w_+)c^* \big) \\
I^{(2)}_{\mr{matter}}(Q,Q) &= \int \frac 14 \dvol (Q_+,Q_+)(\psi_-^*,\psi_-^*)(w_-^* \wedge w_-^*)
\end{align*}
if $Q=Q_+ \otimes w_+$ is a non-zero element of $S_+ \otimes W$. \chris{missing thing here: trivialising those wedge pairs, or equivalently restricting $\Gamma(-,-)$ from 6d to 4d.}
\end{prop}

@@

\chris{that term should correspond to an isomorphism between the two copies of $\gg \oplus \gg[-1] \oplus U[-1]$ in the BV complex.  Fields that survive will be $c, A_{0,1}, \phi_1,\phi_2, \psi_+$, then a single scalar from $\phi$, a single $(0,1)$-form from $\lambda_-$ and a single scalar from $\lambda_+$, along with anti-fields.  The terms that will contribute to the deformation of the differential will be an $A^*\lambda_-$ and a $\phi_2^* \lambda_+$ term from $I^{(1)}_{\mr{gauge}}$, a $\phi^*\psi_+$ term from $I^{(1)}_{\mr{matter}}$, a $c^*\phi_1$ term from $I^{(2)}_{\mr{gauge}}$, and a $\psi_-^*\psi_-^*$ term from $I^{(2)}_{\mr{matter}}$.}
\end{proof}
